---
title: "Search term generation"
author: "Alex Fradera"
date: "15/06/2021"
output: 
  html_document: 
    keep_md: yes
---




```{r write_shortlist, eval=FALSE, include=TRUE}

# record this search into a text file
write_search(
  grouped_terms,
  languages="English",
  exactphrase=TRUE,
  stemming=FALSE, # DECISION: stem or not stem?
  closure="left",
  writesearch=TRUE
)

cat(read_file("search-inEnglish.txt"))
```



## Grouping with litsearchr

The recommendation is to do this by hand - pick out the terms from the list and organise them under your themes. For simplicity I think this is easier to do outside of the R environment (hence extracting terms in the X_possible_terms.txt)




*Note:* in fact some of the screeners names will need to be amended with wildcards.

## Putting search terms into readable contexts

### EBSCO Host

```{r make_ebsco_friendly}
s_screen_title <-  str_c("TI (",screen_referents,")")
s_screen_abstract <-  str_c("AB (",screen_referents,")")
  s_screen_testmeasures  <-  str_c("TM (",screen_referents,")")

```


# Finalise everything

```{r write_shortlist2, eval=FALSE, include=TRUE}

# record this search into a text file
final_search <- write_search(
  TO_DEFINE,
  languages="English",
  exactphrase=TRUE,
  stemming=FALSE, # DECISION: stem or not stem?
  closure="left",
  writesearch=FALSE
)

final_search
```

### Feeding this back in to pubmed

We get a new search, which we save in as new_results:

```{r import_new}
new_results <- import_results(file="new_pubmed.nbib")
```


```{r find_discrepancies}
focus %>%
  mutate(in_new_results=title %in% new_results[, "title"]) ->
  focus

excluded_articles <- focus %>%
  filter(!in_new_results) %>%
  select(title, keywords)

```

```{r write_discrepancies, eval=FALSE, include=TRUE}
 write.csv(excluded_articles, file = "excluded_articles.csv")
```




```{r checking_importants}
important_titles <- c(
  "Screening for pain in patients with cognitive and communication difficulties: evaluation of the SPIN-screen",
  "Pain and the Montreal Cognitive Assessment (MoCA) in Aging",
  "Disruption of cognitive function in Fibromyalgia Syndrome",
  "Cognitive Function Impairment in Patients with Neuropathic Pain Under Standard Conditions of Care",
  "Validity and reliability of the clock drawing test as a screening tool for cognitive impairment in patients with fibromyalgia",
  "Tales of the boogeyman"
)

data.frame(check_recall(important_titles, new_results[, "title"]))
```

